\documentclass[11pt]{amsart}

\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{thmtools}
\usepackage{enumitem}
\usepackage{tikz-cd}
\usepackage{hyperref}
\usepackage[nameinlink]{cleveref}

% % Theorem environments
\declaretheorem[numberwithin=section]{theorem}
\declaretheorem[style=plain, sibling=theorem]{lemma, proposition, corollary}
\declaretheorem[style=definition]{definition, example, condition}
\declaretheorem[style=remark]{remark, note, observation, todo}


\title{April 17, 2026}


\begin{document}
\maketitle

I had a regular team seminar in this morning.
I expected that I have a talk today, but (fortunately) Dr. Seonhwa Kim gave a talk about his recent reserch.
It was about ED-rigidicy for nonconvex polyhedra.
I record short review for it for the future.

Suppose that we have a 3-dimensional polyhedron in Eulidiean space and we know lengths of all the edges and all the dihedral angles.
In this situation, the question is that, whether this polyhedron is geometrically rigid or not, i.e., every polyhedron with the same edge lengths and dihedral angles are congruent.
It is well-known that the answer is yes for convex polyhedra, but it is not known for nonconvex ones.
Seonhwa Kim proved that the answer is also yes for nonconvex ones adapting the notion of rigid vertices.

The vertex $v$ is called \emph{rigid} if $\mathrm{nt}(v) \leq 3$ where $\mathrm{nt}(v)$ is the number of triangles among neighboring faces of $v$.
The number 3 is related to the fact that if we know all the lengths of the link of a vertex $v$, then we know all the facial angles if $\mathrm{nt}(v) \leq 3$.
There is a proposition which states that There exists a rigid vertex for any polyhedra.

He proved the theorem by using induction on the nubmer of vertices of a polyhedron.
At a rigid vertex $v$, by removing the ``cone'' of $v$ from the given polyhedron we can remove one vertex from it.
The point is that, we know all the edge lengths and dihedral angles of the link of $v$, and that the remaining polyhedron is also in ED condition.
The caution is that, we may add edges and faces when we do remove, and how they are added is depending on the geometric conditon of the polyhedron, not the combinatorial one.
In other words, the statement that we have a polyhedron after removing the cone is not free, it is a corollary of the\emph{Steinitz theorem}.

\par\vspace{1em}

After the talk, I went to the hairshop for cutting my hair. 
Then I first reviewed updated papers from arXiv, and then I checked the generated feedback file that codex generated.
It reports that there were lots of typos, wrong article usage (still), and non idiomatic phrases.
I again think that I should a find a way to become accustomed to idioms, I will consult a plan with GPT in this weekend.

\par\vspace{1em}

After then I tried to my own job .. from 6 pm.

Here is the most important TODO list:
\begin{itemize}
    \item To figure out relations between $z$, $w$-variables and McPhail-Snyder's variable explicitly.
    If we do then we may be able to write coefficients of the $R$-matrix used in McPhail-Snyder's paper in terms of $z$,$w$-varaibles.
    It is expected to give us better understandings on the volume conjecture.
    
    \item To review the proof that the Reidemeister torsion is a quantum invariant.
    More precisely, the double construction used in the proof should be reviewed, since I have more insights than before.

    \item To make a correct setting for the theorem about relation between quantum double and the Yetter--Drinfel'd module with automorphism construction by Garoufalidis and Kashaev.
    We must choose convention for left/right module/comodule setting.

    \item To write a paper based on my thesis; clored Jones polynomials of $2n$-plat.
    We may need better understanding for infinite-dimensional $R$-matrices and related invariants.
\end{itemize}

To attack the first problem ($z$,$w$ variables) I first find references for computing such variables in terms of $\mathbb{C}^2$ vector decorations.
There are three references: \cite{KKY-2023-Octa2}, \cite{Zickert-2009-Cvol}, and \cite{GTZ-2015-SLnCvol}.
As expected, we needed more details of the Ptolemy variety.
The first attempt to understand this was to write concrete relation between the Ptolemy relation and the Pl\"ucker relation.

The following is from this \href{https://web.evanchen.cc/notes/MIT-18-217.pdf}{NOTE}.
Let $A=(a, b)$ be a point on $\mathbb{R}^2$.
If we identify $\mathbb{R}^2$ with $\mathbb{C}$, then one can associate $A$ to a complex point on the unit disk
\[
    \frac{z^2}{|z|^2} = \frac{z}{\overline{z}} \in \mathbb{C}
\]
where $z = a + b\sqrt{-1} \in \mathbb{C}$.


For two points $A_i = (a_i, b_i)$ and $A_j = (a_j, b_j)$, the Eulidean distance between two points can be computed as follows.
\begin{align*}
    |A_i - A_j| & = \left| \frac{z_i}{\overline{z_i}} - \frac{z_j}{\overline{z_j}} \right| \\
    & = \left| \frac{z_i \overline{z_j} - \overline{z_i}z_j}{\overline{z_i} \overline{z_j}} \right| \\
    & = \frac{1}{|z_i| |z_j|} \left| (a_i + b_i\sqrt{-1})(a_j - b_j\sqrt{-1}) - (a_i - b_i\sqrt{-1})(a_j + b_j\sqrt{-1}) \right| \\
    & = \frac{2}{|z_i| |z_j|} \det \begin{bmatrix}
        a_i & a_j \\ b_i & b_j
    \end{bmatrix}.
\end{align*}
Thus, the Ptolemy relation can be interpreted as the Pl\"ucker relation with the map
\[
    \mathbb{R}^2 \setminus \{ (0,0) \} = \mathbb{C}^\times \xrightarrow{z/|z|} S^1 \xrightarrow{(-)^2} S^1.
\]

AI explains this relation might be extended to any points on a conic.
More precisely, a conic, a curve in $\mathbb{P}^2$ defined by a zero locus of degree 2 homogeneous polynomial, is isomorphic to $\mathbb{P}^1$ over an algebraically closed field.
The map between them is defined considering a line passing a fixed point on the curve.
The line intersects with only one other point with the curve, this gives a bijection between $\mathbb{P}^1$ and points on the curve.

\par\vspace{1em}




\bibliographystyle{amsalpha}
% \nocite{*}
\bibliography{bibliography}
\end{document}
