\documentclass[11pt]{amsart}

\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{thmtools}
\usepackage{enumitem}
\usepackage{tikz-cd}
\usepackage{hyperref}
\usepackage[nameinlink]{cleveref}
\usepackage[backend=biber, doi=true, url=true, style=alphabetic]{biblatex}
\addbibresource{bibliography.bib}

% % Theorem environments
\declaretheorem[numberwithin=section]
{theorem}
\declaretheorem{lemma, proposition, corollary}[
style=plain,
sibling=theorem,
]
\declaretheorem[style=definition]
{definition, example, condition}
\declaretheorem[style=remark]{remark, note, observation}


\title{Review on \\ McPhail--Snyder's work}
\author{knottedtail}
\address{Chonnam University}
\email{philip94@snu.ac.kr}
\date{13 April, 2026}


\begin{document}

\begin{abstract}
    Here, we review all the paper written by McPhail-Snyder.
\end{abstract}

\maketitle

\section{Overview}

There are 8 papers written by McPhail--Snyder.
The following is citation of those papers in the order of decreasing time of the first uploaded on arXiv.
\begin{itemize}
    %2601.05136
    \item \cite{McPhailSnyder-2026-stateintegral}: \citetitle{McPhailSnyder-2026-stateintegral}
    %2509.02365
    \item \cite{McPhailSnyder-2025-quantization_tangle}: \citetitle{McPhailSnyder-2025-quantization_tangle}
    %2509.02354
    \item \cite{McPhailSnyder_Reshetikhin-2025-cyclic_modules} (with Nicholas Reshetikhin): \citetitle{McPhailSnyder_Reshetikhin-2025-cyclic_modules}
    %2404.19155
    \item \cite{McPhailSnyder-2025-octahedral_coordinates}: \citetitle{McPhailSnyder-2025-octahedral_coordinates}
    %2203.06042
    \item \cite{McPhailSnyder-2026-hyperbolic_octa_quantum}: \citetitle{McPhailSnyder-2026-hyperbolic_octa_quantum}
    %2108.06561
    \item \cite{Chen_McPhailSnyder_Morrison_Snyder-2021-Kashaev_Reshetikhin} (with Kai-Chieh Chen, Scott Morrison and Noah Snyder): \citetitle{Chen_McPhailSnyder_Morrison_Snyder-2021-Kashaev_Reshetikhin}
    \item \cite[Thesis]{McPhailSnyder-2021-thesis}: \citetitle{McPhailSnyder-2021-thesis}
    %2005.01133
    \item \cite{McPhailSnyder-2022-holonomy_torsion}: \citetitle{McPhailSnyder-2022-holonomy_torsion}
    %1805.00575
    \item \cite{McPhailSnyder_Miller-2020-planar_diagrams} (with Kyle. A. Miller): \citetitle{McPhailSnyder_Miller-2020-planar_diagrams}
\end{itemize}

In this paper, we focus on reviewing only the following papers related to the octahedra decompositon of knot complements and quantum invrariants:
\begin{center}
    \cite{McPhailSnyder-2025-quantization_tangle}, 
    \cite{McPhailSnyder_Reshetikhin-2025-cyclic_modules}
    \cite{McPhailSnyder-2025-octahedral_coordinates},
    \cite{McPhailSnyder-2026-hyperbolic_octa_quantum}, 
    \cite{McPhailSnyder-2021-thesis},
    \cite{McPhailSnyder-2022-holonomy_torsion}.
\end{center}
We are using common definitions and recall results on the above paper appropriately.
Let us conclude the overview by providing short summary for remaining papaers.

\medskip
\noindent \textbf{Review on \cite{McPhailSnyder_Miller-2020-planar_diagrams}}.
This paper aims to generalize quantum invariants of planar graph obtained from the representation of quantum group.

The authors consider \textit{virtual graphs}, which are (stable) equivalence classes of graphs embedded in a fixed surface.
The local topology of virtual graphs forms a \texttt{planar diagram category}, and quantum invariants are regarded as functors from this category to the category of modules over a quantum group.
In this way, the author seems to generalize the flow polynomial, $S$-polynomial, and $\mathfrak{sl}(N)$ Penrose polynomial.

\medskip
\noindent

\section{Notes}

\begin{center}
    \cite{McPhailSnyder-2025-quantization_tangle}
\end{center}

A list of quesetions:
\begin{itemize}
    \item Why Chern-Simons invariant $\mathcal{I}(L, \rho, \mathfrak{s})$ is called a 'line bundle' over representation variaty?
    \item "Choice of root of the unity" $\rightarrow$ "Choice of $\log$-parameter $\mathfrak{s}$"?
\end{itemize}

Observations:
\begin{itemize}
    \item page 4: (When computing $\mathcal{I}$ using the ideal triangulation) adding up lifted dilogarithms on \textit{flattening} $\rightarrow$ only depends on the choice of the $\log$-parameter
    \item page 5: (GOAL) the braiding (without phase ambiguity) -> tangle invariant, to explain the results of \cite{McPhailSnyder_Reshetikhin-2025-cyclic_modules} in terms of CS theory and hyperbolic geometry.
    \item page 5: colors on segments and regions $\Rightarrow$ 2-category is used instead of monoidal category
    \item page 6: 2-morphims = colored tangles, 1-morphisms = ``composition of SL2 matrices'' where each morphism $g \in \mathrm{SL}_2$ represents $u \rightarrow g\cdot u$ for a given object $u \in \mathbb{C}^2 \setminus \{ 0\}$.
    \item page 6: any monoidal cat is a 2-category
    \item page 8: KBSM is related to the \textit{cobraiding} on $\mathrm{SL}_q(2)$; (the author already knows this relation!).
    \item page 8: \cite{Chen_McPhailSnyder_Morrison_Snyder-2021-Kashaev_Reshetikhin} used already braiding on \( U_\xi / \ker{\xi} \) ! but there is a drawback that the geometric meaning and the relation between the Kashaev invariant is missing.
    \item Section 2: 
    This section provides viewpoint on quantum/classical gauge theory.
    The authors consider the classical Chern-Simons invariant as a holomorphic section $\mathcal{I}(M_K)$ of the knot exterior $M_K$ of a given framed oriented knot $K$ in $S^3$ (Proposition 2.2).
    This section is defined for a line bundle over the \textit{decorated} representation variety $R(M_K)$ but the invariant is invariant under the choice of decorations.
    Similarly, the author claim that he (will) define a section for the \textit{vector} bundle over the decorated representation variety.
    \item page 16: To keep track of change-of-basepoint data, we use additional colors called \emph{shadows}.
\end{itemize}

\begin{remark}
    Let $\mathcal{M} := \mathbb{C}^2$, the universal cover of $\mathcal{X} = (\mathbb{C}^{\times})^2$ with the projection map which is the exponential map.
    Regarding the trivial bundle $\mathcal{M} \times \mathbb{C}$, one might regard a section of this bundle as a functional on $\mathcal{M}$.
    Moreover, if we can extend the action of $\mathbb{Z}^2 \cong \pi_1(\mathcal{X})$ on $\mathcal{M}$ to this bundle, then we have a quotient bundle $(\mathcal{M} \times \mathbb{C})/\mathbb{Z}^2$ over $\mathcal{X}$.
    In other words, we have the following commutative diagram.
    \[
        \begin{tikzcd}
        M \times \mathbb{C} \arrow[r, two heads] \arrow[d, two heads]
        & (M \times \mathbb{C})/\mathbb{Z}^2 \arrow[d] \\
        M \arrow[r, two heads]
        & X
        \end{tikzcd}
    \]
    and we regard \( M \times \mathbb{C} \) as a pull-back bundle of \( (M \times \mathbb{C})/\mathbb{Z}^2 \).

    For any (holomorphic) section $f$ of \( (M \times \mathbb{C})/\mathbb{Z}^2 \) then we have a (holomorphic) pull-back section of $M \times \mathbb{C}$, equivalent to a functional on $M$ with the restriction induced by the action of $\mathbb{Z}^2$.

    In particular, the action considered in the reference is that
    \[
        (a,b) \cdot (x, y, z) = (x+a, y+b, e^{2\pi i(bx - ay)} z),
    \]
    hence the section $f$ satisfies that 
    \[
        f(x+a, y+b) = e^{2\pi i(bx - ay)} f(x,y),
    \]
    which is called the \emph{quasi-periodicity relation}.
\end{remark}


\printbibliography
% \bibliographystyle{alphabetic-side}
% % \nocite{*}
% \bibliography{bibliography}

\end{document}
